\vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{ We are grateful for various people from various university, and several conferences for useful feedback. }

### 2024-07-10 manuscript/main.tex
modified:   analysis/RD design analysis.Rmd 	modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	modified:   result_tables/rdd_result_summary.tex

  \textbf{Keyword}: Marketing Strategy, Platforms, Platform-Mediated Consolidation, Real Estate Brokerage

  \textbf{JEL} Classification Codes: D4, L1, L8, R3
\end{singlespace}
\thispagestyle{empty}

@@

\begin{figure}[ht]
    \centering
    \subfloat[RDD plot with first order polynomial]{\includegraphics[width=0.5\textwidth]{../figures/RD_Plot_1st_Order.pdf}\label{fig:RD_Plot_1st_Order}}
    \hfill % Adds horizontal space between figures
    \subfloat[RDD plot with second order polynomial]{\includegraphics[width=0.5\textwidth]{../figures/RD_Plot_2nd_Order.pdf}\label{fig:RD_Plot_2nd_Order}}
    \hfill % Adds horizontal space between figures
    \subfloat[RDD plot with third order polynomial]{\includegraphics[width=0.5\textwidth]{../figures/RD_Plot_3rd_Order.pdf}\label{fig:RD_Plot_3rd_Order}}
    \caption{RDD design}
    \label{fig:RD_design}
\end{figure}

@@

    Note that the code book of the variables can be seen in the Appendix \ref{tab:codebook}
    \end{tiny}
\end{table}

>>>>

  \textbf{Keyword}: Real estate brokerage, Platform-mediated consolidation, Offline store operation, Franchise network

  \textbf{JEL} Classification Codes: R30, R31, L85, L86
\end{singlespace}
\thispagestyle{empty}

@@

\begin{figure}[ht]
    \centering
    \subfloat[RDD plot with first order polynomial]{\includegraphics[width=0.5\textwidth]{../figures/RD_Plot_1st_Order.pdf}\label{fig:RD_Plot_1st_Order}}
    \hfill % Adds horizontal space between figures
    \subfloat[RDD plot with second order polynomial]{\includegraphics[width=0.5\textwidth]{../figures/RD_Plot_2nd_Order.pdf}\label{fig:RD_Plot_2nd_Order}}
    \hfill % Adds horizontal space between figures
    \subfloat[RDD plot with third order polynomial]{\includegraphics[width=0.5\textwidth]{../figures/RD_Plot_3rd_Order.pdf}\label{fig:RD_Plot_3rd_Order}}
    \caption{RDD with Different Polynomial Orders}
    \label{fig:RD_design}

    Note that the running variable is divided into 40 bins, considering only the samples within the specified bandwidth. The polynomial order for the RDD analysis ranges from 1 to 3. Each plot illustrates the relationship between the community transaction revenue and the nearest distance to Lianjia's stores, with the discontinuity point at the cutoff.
\end{figure}

@@

    Note that the code book of the variables can be seen in the Appendix \ref{tab:codebook} and with or without lianjia represent whether there are Lianjia's offline stores within the influential radius.
    \end{tiny}
\end{table}
